HealpixNet: Efficient spherical Convolutional Neural Network with Healpix sampling for cosmological applications

### 2018-08-03 scnn.tex
composition operator

Given a map $\X \in \R^{N_{pix} \times F}$, the neural network is computing $\y = NN_\theta(\X) \in R^{N_{classes}}$, where $NN$ is a composition of the above layers and $\theta$ is the set of all trainable parameters.
An example network can be defined as
\begin{equation}
NN = SM \circ FC \circ \sigma \circ FC \circ ST \circ \sigma \circ GC \circ P \circ \sigma \circ BN \circ GC,
\end{equation}
\TK{what is the meaning of $\circ$ here?}\nati{where $\circ$ is the composition operator between two layers.}
The number of features $F$ depends on the data at hand. For the CMB radiation temperature, $F = 1$. For observations in radio frequencies, $F$ would be equal to the number of surveyed frequencies. $F$ might also be the number of slices in the radial direction.
The loss function $\ell(\y) = \ell(NN_\theta(\X))$ is a measure of how good the prediction $\y$ is for the sample $\X$. For a classification task, the loss is usually taken to be the cross-entropy
\begin{equation*}
	\ell(\y) = -\log(y_i),
\end{equation*}
where $i$ is the correct class label.
The parameters $\theta$ of the neural network are optimized to minimize the loss over the training dataset $\left\{ \X_i \right\}_{i=1}^{N_{samples}}$:
\begin{equation*}
	\hat{\theta} = \argmin_\theta \sum_{i=1}^{N_{samples}} \ell(NN_\theta(\X_i)).
\end{equation*}
The same architecture with different loss function can also be used for parameter regression \citep{fluri2018deep,gupta2018nongaussianinformation}.
The optimization is performed by computing an error gradient w.r.t.\ all the parameters by back-propagation and updating them with a form of stochastic gradient descent (SGD):
\begin{equation*}
	\theta \leftarrow \theta - \frac{\eta}{|\B|} \sum_{i \in \B} \frac{\partial \ell(NN_\theta(\X_i))}{\partial \theta} ,
\end{equation*}
where $\eta$ is the learning rate, and $\B$ is the set of indices in a mini-batch. Batches are used instead of single samples to gain speed by exploiting the parallelism afforded by modern computing platforms.

>>>>

Given a map $\X \in \R^{N_{pix} \times F}$, the neural network is computing $\y = NN_\theta(\X) \in R^{N_{classes}}$, where $NN$ is a composition of the above layers and $\theta$ is the set of all trainable parameters.
An example network is
\begin{equation*}
NN = SM \circ FC \circ \sigma \circ FC \circ ST \circ \sigma \circ GC \circ P \circ \sigma \circ BN \circ GC,
\end{equation*}
where $\circ$ denotes composition, i.e., $f \circ g = f(g(\cdot))$.
The number of features $F$ depends on the data at hand. For the CMB radiation temperature, $F = 1$. For observations in radio frequencies, $F$ would be equal to the number of surveyed frequencies. $F$ might also be the number of slices in the radial direction.
The loss function $\ell(\y) = \ell(NN_\theta(\X))$ is a measure of how good the prediction $\y$ is for the sample $\X$. For a classification task, the loss is usually taken to be the cross-entropy
\begin{equation*}
	\ell(\y) = -\log(y_i),
\end{equation*}
where $i$ is the correct class label.
The parameters $\theta$ of the neural network are optimized to minimize the loss over the training dataset $\left\{ \X_i \right\}_{i=1}^{N_{samples}}$:
\begin{equation*}
	\hat{\theta} = \argmin_\theta \sum_{i=1}^{N_{samples}} \ell(NN_\theta(\X_i)).
\end{equation*}
The same architecture with different loss function can also be used for parameter regression \citep{fluri2018deep,gupta2018nongaussianinformation}.
The optimization is performed by computing an error gradient w.r.t.\ all the parameters by back-propagation and updating them with a form of stochastic gradient descent (SGD):
\begin{equation*}
	\theta \leftarrow \theta - \frac{\eta}{|\B|} \sum_{i \in \B} \frac{\partial \ell(NN_\theta(\X_i))}{\partial \theta} ,
\end{equation*}
where $\eta$ is the learning rate, and $\B$ is the set of indices in a mini-batch. Batches are used instead of single samples to gain speed by exploiting the parallelism afforded by modern computing platforms.
